Figures for Paper

### 2021-10-01 paper_figures.Rmd
Update paper_figures.Rmd

WAFFLES 
```{css, echo = FALSE}
h1, #TOC>ul>li {
  color: #000000;
    font-weight: bold;
}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
knitr::opts_chunk$set(
  comment = '', fig.width = 9, fig.height = 9
)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here",
       "ggthemes",
       "ggrepel",
       "DESeq2",
       "patchwork",
       "rstatix",
       "ggeasy")
```

@@

@@

nmd_plot_chx = ggbarplot(for_bar_plot,
                     x = 'Gene',
                     add = c("mean_se","jitter"),
                     y = 'Value',
                     color = 'Treatment',
                     position = position_dodge(0.8),
                     dot.size = 10) +
  scale_y_continuous() + 
  ggpubr::theme_pubr() + stat_pvalue_manual(stattest, label="p.signif" , x = "Gene")
plot(nmd_plot_chx)

@@

```{r}
guide_strength = fread(file.path(here::here(),"data","different_guides_cryptic_expression.csv"))

guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i5W") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("NCRM5") +
         theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))

guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i11w_repeat") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild")) %>%
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "value",
              fill = 'variable',
              color = 'variable',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
      scale_color_manual(
        values = c("#1C2617","#262114","#262114")
    ) +
        scale_fill_manual(
        values = c("#1576b8","#eb7f3f","#975452")
    ) +
    scale_y_continuous(labels = scales::percent) +
  ggtitle("WTC11") +
           theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))
```

@@

ggplot(agg, aes(y=Value, x=Treatment)) +
  geom_line(size = 2,mapping = aes(x=Treatment, y=Value,
                          linetype=Line_Group, group=Gene,color = Color_Group), size=1)+
  geom_errorbar(limits, 
                position=dodge, 
                width=0.24,
                size = 1.1)+
  xlab("") +
  ylab("") +
  ggpubr::theme_pubr()+
  scale_y_continuous(labels = scales::percent_format(scale = 1))+
  scale_colour_viridis_d(begin=0, end=1) +
  labs(linetype = "") +
  theme(axis.ticks.length=unit(0.1,"inch"),
        axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))

>>>>

```{css, echo = FALSE}
h1, #TOC>ul>li {
  color: #000000;
    font-weight: bold;
}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
knitr::opts_chunk$set(
  comment = '', fig.width = 9, fig.height = 9
)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "ggnewscale",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here",
       "ggthemes",
       "ggrepel",
       "DESeq2",
       "patchwork",
       "rstatix",
       "ggeasy")
```

@@

```{r}
std <- function(x) sd(x)/sqrt(length(x))

@@

sum_for_bar_plot <- for_bar_plot %>% 
  group_by(Gene,Treatment) %>% 
  summarize(mean = mean(Value),sem = std(Value))

ggplot(sum_for_bar_plot) +
  geom_col(aes(x = Gene, fill = Treatment, y = mean),position = "dodge2",color = 'black') +
  scale_fill_manual(values = c("#F9AC66","#B4C640")) +
  new_scale_fill() +
  geom_errorbar(aes(x = Gene, ymin = mean - sem, ymax = mean + sem),
                position = "dodge2",size = 1.8) +
  geom_point(data = for_bar_plot, aes(x = Gene, fill = Treatment, y = Value),
             pch = 21, 
             size = 4, stroke = 1.5,
             position = position_jitterdodge(jitter.width = 0.2)) +
  scale_fill_manual(values = c("#000000","#000000")) +
  ggpubr::theme_pubr() + 
  theme(axis.ticks.length=unit(0.1,"inch"),
        axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))

@@

```{r}
guide_strength = fread(file.path(here::here(),"data","different_guides_cryptic_expression.csv"))
std <- function(x) sd(x)/sqrt(length(x))

ncrm5 <- guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i5W") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild"))
sum_df_ncrm5 <- ncrm5 %>% 
  group_by(condition, variable) %>% 
  summarize(mean = mean(value),sem = std(value))

ggplot(sum_df_ncrm5) + 
  geom_col(aes(x = condition, fill = variable, y = mean),position = "dodge2",color = 'black',stroke = 1.5) +
    scale_fill_manual(values = c("#1576b8","#eb7f3f","#975452")) +
    geom_errorbar(aes(x = condition, ymin = mean - sem, ymax = mean + sem),
                position = "dodge2",size = 1.8) +
    new_scale_fill() +
  geom_point(data = ncrm5, aes(x = condition, fill = variable, y = value),
             pch = 21, 
             size = 4, stroke = 1.5,
             position = position_jitterdodge(jitter.width = 0.2))  +
  scale_fill_manual(values = c("#000000","#000000","#000000")) +

  ggpubr::theme_pubr() + 
  scale_y_continuous(labels = scales::percent) +
  ggtitle("NCRM5") +
         theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))

wtc11 <- guide_strength %>% 
  melt() %>% 
  filter(`cell line` == "i11w_repeat") %>% 
   mutate(condition = fct_relevel(condition,
                              "control","tdp43_mild"))
sum_df_wtc11 <- wtc11 %>% 
  group_by(condition, variable) %>% 
  summarize(mean = mean(value),sem = std(value))

ggplot(sum_df_wtc11) + 
  geom_col(aes(x = condition, fill = variable, y = mean),position = "dodge2",color = 'black',stroke = 1.5) +
    scale_fill_manual(values = c("#1576b8","#eb7f3f","#975452")) +
    geom_errorbar(aes(x = condition, ymin = mean - sem, ymax = mean + sem),
                position = "dodge2",size = 1.8) +
    new_scale_fill() +
  geom_point(data = wtc11, aes(x = condition, fill = variable, y = value),
             pch = 21, 
             size = 4, stroke = 1.5,
             position = position_jitterdodge(jitter.width = 0.2))  +
  scale_fill_manual(values = c("#000000","#000000","#000000")) +

  ggpubr::theme_pubr() + 
  scale_y_continuous(labels = scales::percent) +
  ggtitle("WTC11") +
         theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))
```

@@

ggplot(agg, aes(y=Value, x=Treatment)) +
  geom_line(size = 2,mapping = aes(x=Treatment, y=Value,
                          linetype=Line_Group, group=Gene,color = Color_Group), size=1)+
  geom_errorbar(limits, 
                position=dodge, 
                width=0.24,
                size = 1.1)+
  xlab("") +
  ylab("") +
  ggpubr::theme_pubr()+
  scale_y_continuous(labels = scales::percent_format(scale = 1))+
  labs(linetype = "") +
  scale_color_manual(values = c("#E1BE6A","#CD5582","#A987E8"))+
  theme(axis.ticks.length=unit(0.1,"inch"),
        axis.line = element_line(colour = 'black', size = 1.5),
        axis.ticks = element_line(colour = "black", size = 2))
